### 2018-11-21 draft.Rmd
correct bibliography

---
bibliography: bibliography.bib
editor_options:
  chunk_output_type: console
output:
  word_document:
    df_print: kable
    fig_caption: yes
    reference_docx: reference.docx
---

@@

Almost all speakers of Andi and other Andic languages speak Avar and Russian in addition to their mother tongue. Avar was the major local lingua franca in this area before the introduction of Russian and, to a certain extent, still is. Speakers of Andic (as well as speakers of Tsezic) languages use it to communicate with each other and with local Avars. The language is also taught in school during the course called "native language" (*rodnoy yazyk* in Russian). For speakers of Andi, Avar is the language of literacy. Before the introduction of modern technology like computers and cellphones, they would write letters to each other in Avar. Currently, they use the extended Cyrillic script of Avar (featuring, among other things, special diacritics for ejective consonants) to write their own language. Russian was introduced as the language of administration and education in the first half of the 20th century and subsequently has strengthened its position throughout the republic, cf. [@dobrushina11]. Andi speakers use it to communicate with people from other regions of Daghestan where Avar is not spoken.

>>>>

---
bibliography: bibliography.bib
csl: deutsche-sprache.csl
always_allow_html: yes
editor_options:
  chunk_output_type: console
output:
  word_document:
    df_print: kable
    fig_caption: yes
    reference_docx: reference.docx
---

@@

Almost all speakers of Andi and other Andic languages speak Avar and Russian in addition to their mother tongue. Avar was the major local lingua franca in this area before the introduction of Russian and, to a certain extent, still is. Speakers of Andic (as well as speakers of Tsezic) languages use it to communicate with each other and with local Avars. The language is also taught in school during the course called "native language" (*rodnoy yazyk* in Russian). For speakers of Andi, Avar is the language of literacy. Before the introduction of modern technology like computers and cellphones, they would write letters to each other in Avar. Currently, they use the extended Cyrillic script of Avar (featuring, among other things, special diacritics for ejective consonants) to write their own language. Russian was introduced as the language of administration and education in the first half of the 20th century and subsequently has strengthened its position throughout the republic, cf. [@dobrushina13, @dobrushina18]. Andi speakers use it to communicate with people from other regions of Daghestan where Avar is not spoken.
